Solutions to Integer Programming from Quantum Annealing

### 2020-05-08 paper/main.tex
some discussion and method (marked in blue)

In quantum annealing, the ground state of the problem Hamiltonian is obtained from the evolution of a time-dependent Hamiltonian,
\begin{equation}
H(s) = A(s) H^{\textrm{init}} + B(s) H^{\textrm{problem}},
\end{equation}
where $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, and $H^\textrm{problem}$ is given by Eq.~(\ref{eq:matrix_form}) for the MDS application. The variable $s\in [0, 1]$ is the normalized annealing time and is allowed to vary between 1$\mu s$ to 2$ms$ on the DWave. On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits. In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in addition to the effects of applying positive and negative offsets. Note that due to the way the offsets are implemented on the hardware level, systematic errors are introduced since the initial and final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets. Fig.~\ref{fig:anneal_schedule} shows the maximum offset that we use for the study, which translates to approximately (due to non-linearity) a 5\% advancement (blue) or delay (red) in the schedule.

@@

@@

>>>>

In quantum annealing, the ground state of the problem Hamiltonian is obtained from the evolution of a time-dependent Hamiltonian,
\begin{equation}
H(s) = A(s) H^{\textrm{init}} + B(s) H^{\textrm{problem}}, \label{eq:tdhamiltonian}
\end{equation}
where $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, and $H^\textrm{problem}$ is given by Eq.~(\ref{eq:matrix_form}) for the MDS application. The variable $s\in [0, 1]$ is the normalized annealing time and is allowed to vary between 1$\mu s$ to 2$ms$ on the DWave. On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits. In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in addition to the effects of applying positive and negative offsets. Note that due to the way the offsets are implemented on the hardware level, systematic errors are introduced since the initial and final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets. Fig.~\ref{fig:anneal_schedule} shows the maximum offset that we use for the study, which translates to approximately (due to non-linearity) a 5\% advancement (blue) or delay (red) in the schedule.

@@

{\color{blue} (I tried to write something here...) Intuitively, we want the system to explore larger state space to increase the probability for the system to reach the final ground state. That is, we want the system to have ergodicity to avoid MBL. On the other hand, decoherence in the hardware leads to the loss of quantum information. It is desirable to minimize the effect of relaxation. The interplay between these two competing effects causing the complications in the results of annealing schedule offsets. Insights can be obtained by looking at the mutual information $I(A:B)=S(\rho_A)+S(\rho_B)-S(\rho_{A,B})$, which quantifies how many bits of quantum information is communicated between partition A and partition B of the total system. $S(\rho)=-\mbox{Tr}\rho \log_2 \rho$ is the von Neumann entropy of density matrix $\rho$.
(Should we talk about mutual information here? or in the latter MBL part? )}

@@

{\color{blue}

To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
\begin{align}
\partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
\end{align}
where $\rho (t)$ is the density matrix at time $t$. $H(t)$ is the time-dependent Hamiltonian in Eq.~(\ref{eq:tdhamiltonian}). $[,]$ denotes the Lie bracket. $L_j$ are the Lindblad operators for decoherence. $\{, \}$ denotes the anti-commutator. In this study we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits. The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma = 1/T_1$ is the decoherence rate for relaxation time $T_1$. For simplicity we assume all qubits having the same relaxation time. The initial condition is the Gibbs canonical ensemble
\begin{equation}
\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} .
\end{equation}
The probability to get the ground state at measurement is
\begin{align}
P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
\end{align}
where the projection operator onto the degenerated ground states subspace is defined as $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $. Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.

}
